\bf\mftitle

### 2011-02-16 doc/jInfer/basicxsd/basicxsd.tex
Documentation: BasicXSDExporter.

Before we describe the export of elements, let's take a look on how we define elements and their attributes using XSD language.\\

@@

\section{Known problems and limitations} \label{section:problems}

This section describes some limitations of XSD export and some known problems, which occur in some specific cases of input grammar.

>>>>

Before we describe the export of elements, let's take a look on how we define elements and their attributes using XSD language. This subsection covers only XSD features that the exporter supports. For list of supported features, see TODO ref.\\

@@

\section{Known issues and limitations} \label{section:problems}

This section describes some limitations of XSD export and some known issues, which occur in some specific cases of input grammar.

\subsection{Supported XSD features} \label{subsection:supportedXSDFeatures}

This module is just basic implementation so many XSD features are not supported. List of supported XSD elements and their attributes follows. Let \code{xs} be XMLSchema namespace.

\begin{itemize}
	\item \code{xs:element} - \code{name}, \code{type}, \code{minOccurs}, \code{maxOccurs}
	\item \code{xs:attribute} - \code{name}, \code{type}, \code{use}
	\item \code{xs:complexType} - \code{name}, \code{mixed}
	\item \code{xs:sequence} - \code{minOccurs}, \code{maxOccurs}
	\item \code{xs:choice} - \code{minOccurs}, \code{maxOccurs}
\end{itemize}
